One part still missing from the analysis of the difference in performance between AV and SV is a measure of the impact on different investors. Investors with different risk aversion will experience different utility effects to the constrained returns of the AV and SV strategies\footnote{As \citet{moreira_volatility-managed_2017} note, "With no leverage limit, percentage utility gains are the same regardless of risk-aversion because investors can freely adjust their average risk exposure."}. I consider a mean-variance investor as in \cite{Kandel1996}, \cite{Campbell2008}, \cite{Ferreira2011}, \cite{Rapach2016}, and others. To measure changes to investor utility from switching between the SV and AV portfolios and due to leverage constraints, I use the difference in certainty equivalent return, CER. The CER change will measure the change in risk-less return an investor demands, given their risk aversion, to use a given portfolio versus another. This can equivalently be though of as a measure of the management fee an investor, given a specific risk aversion, would be willing to pay to have access to an investment fund using AV rather than SV as a signal. CER change is calculated as the difference in risk adjusted return using:
\begin{equation}
\Delta \text{ CER}_{x} = \left(\hat \mu_{r_{x}} - \frac{1}{2}\gamma\hat \sigma^{2}_{r_{x}}\right) - \left(\hat \mu_{r_{y}} - \frac{1}{2}\gamma\hat \sigma^{2}_{r_{y}}\right)
\end{equation}
where $\hat \mu_{r_{x}}$, $\hat \mu_{r_{y}}$, $\hat \sigma^{2}_{r_{x}}$, and $\hat \sigma^{2}_{r_{y}}$ are the means and
variances of the returns to the x and y portfolios and $\gamma$ is the investor risk aversion coefficient. I multiply the gains by 12 to annualize them. All investor risk aversion coefficients from 1 to 5 are tested for investors subject to investment constraints from a limit of 1 to 3 on the market portfolio, no leverage to 200\% leverage.

\bigskip
\centerline{\bf [Place Figure~\ref{fig:cer_loss} about here]}
\bigskip

Figure \ref{fig:cer_loss} shows the decrease in CER, from unconstrained AV or SV management, as leverage constraints are applied to each strategy. CER losses accumulate for the SV managed portfolio sooner than for the AV managed portfolio. This is due to the extreme leverage positions needed for the SV managed portfolio. Across risk aversion coefficients, leverage constraints bite sooner and cut deeper into the SV managed portfolio until both are driven together when no leverage is allowed. The CER of the AV managed strategy starts higher at 7.95\%, 8.98\%, and 9.33\% versus 6.87\%, 7.90\%, and 8.25\% for investors with risk aversion coefficients of 1, 3, and 5. When those investors are subject to 200\% leverage constraint the CERs are 7.96\%, 8.99\%, 9.33\%, versus 6.22\%, 7.05\%, and 7.33\% for SV management. The AV manged portfolio provides the same investor utility while the benefit from the SV managed portfolio decreases by 9.46\%, 10.76\%, and 11.15\%. To incorporate the starting difference in utility I look at the CER gains moving from the SV to AV managed portfolio. 

\bigskip
\centerline{\bf [Place Figure~\ref{fig:cer_gain} about here]}
\bigskip

As shown in figure \ref{fig:cer_gain}, CER gains for the market variance targeting AV managed portfolio are increasing in both risk aversion and leverage use for constrained risk averse mean-variance investors. An investor with a risk aversion coefficient of 2 would capture an annualized CER gain of 1.49 percentage points using 50\% leverage and 1.91 implementing the AV strategy through the 200\% leveraged ETFs. The most risk averse investors subject to a 20\% leverage limit see a CER gain of 1.35 percentage points while the most risk tolerant see a 1.08 percentage points gain. The most risk averse investor, using the highest feasible leverage, realizes a CER gain of over 2 percentage points which translates to a utility increase of 27.4\%. This increase is in the neighborhood of those typically seen from return timing strategies. \citep{campbell1997econometrics,moreira_volatility-managed_2017} Risk averse, mean-variance investors see substantial utility gains switching from the SV to AV managed portfolio and these gains increase with leverage usage. AV management is better, regardless of risk aversion level or leverage constraint.

\bigskip
\centerline{\bf [Place Figure~\ref{fig:cer_gain} about here]}
\bigskip

\subsection{Stochastic Dominance}

Again, there may be some concern about using mean-variance investors. However, it seems reasonable that investors still care about the variance of their portfolio return as the AV management strategy relies on the superiority of the AV signal not on investors taking AV as the measure of risk. However for robustness, I test AV management against SV for a larger class of investors by moving away from the assumption of mean-variance utility using stochastic dominance. As \citet{hadar_rules_1969,hanoch_efficiency_1969,rothschild_increasing_1970,levy_experimental_2002} detail, the use of stochastic dominance tests allow us to make conclusions about the preferred strategy of investors whose expected utility functions differ from simple mean-variance optimization. I use the methods detailed in \citet{vinod_h.d._ranking_2004,vinod_hands-intermediate_2008} to test the stochastic dominance of AV over SV management to the forth order. Second order stochastic dominance, AV over SV management, means that any risk averse investor would prefer AV. \citep{mcfadden_testing_1989,valle_novel_2017} Third order stochastic dominance means that any expected utility investor regardless of the form of the utility function would prefer AV to SV. \citep{whitmore_third-degree_1970,chan_third_2016} At forth order stochastic dominance, in addition to the concept of risk aversion both prudence and temperance are incorporated and all expected-utility theory (EUT) investors prefer AV management to SV. \citep{kimball_standard_1993,noauthor_risk-aversion_nodate} Moreover, investors with non-EUT, e.g. prospect theory, preferences still prefer AV management to SV. \citep{kahneman_prospect_1979} As, \citet{prelec_probability_1998} shows a probability weighting function can be used to incorporate the deviations in preference of non-EUT investors into stochastic dominance analysis.  

Following \citet{vinod_hands-intermediate_2008}, I first calculate kernel smoothed density and cumulative distribution functions (CDFs) for the unconstrained AV and SV managed portfolio return distributions. Figure \ref{fig:kd_graph} shows the density and CDFs estimated for the US equity returns to the buy and hold targeting AV and SV managed portfolios without investment constraints.
\bigskip
\centerline{\bf [Place Figure~\ref{fig:kd_graph} about here]}
\bigskip

%\begin{figure}[htb]
%	\centering
%	\caption{{\bf These figures show the smoothed kernel smoothed density and empirical CDFs calculated for the returns to the AV and SV managed US equity portfolios. These are examples of the estimated distributions are used in the stochastic dominance tests which follow.}} \label{fig:kd_graph}
%	\begin{subfigure}{\textwidth}
%		\input{figures/kd_plots}
%	\end{subfigure}
%	
%	\begin{subfigure}{\textwidth}
%		\input{figures/kd_plots2}
%	\end{subfigure}
%	
%	\begin{subfigure}{\textwidth}
%		\input{figures/kd_plots3}
%	\end{subfigure}
%	
%	\begin{subfigure}{\textwidth}
%		\input{figures/kd_plots4}
%	\end{subfigure}
%\end{figure}
The stochastic dominance tests involve the comparisons of the CDFs of the appropriate order, or power, of the portfolio returns. Generally, the test is a comparison of which distributions CDF sits "to the right" of the other. The CDF "to the right" means the return distribution which has more likely higher values. The portfolio CDFs can now be compared to test stochastic dominance at various orders, but more information on the preferences of investors can be incorporated before performing the tests.

\citet{prelec_probability_1998} defines a flexible function with parameter $\alpha$ controlling the "slope" of the "weight" an investor places on an observed return, ordered from smallest to largest. When $\alpha$ equals zero, investors are EUT-compliant and place equal weight on all observed utilities from returns regardless of size when evaluating two possible portfolios. When $\alpha$ is less than one but greater than zero, investors place greater weight on the lower, negative, realized returns than the higher a result consistent with loss aversion from prospect theory. Figure \ref{fig:sd_ill_graph} shows the relationship between $\alpha$, the ordered cumulative return probability and the weight the investor places on the probability of such a return.
\bigskip
\centerline{\bf [Place Figure~\ref{fig:sd_ill_graph} about here]}
\bigskip

%\begin{figure}[htb]
%	\centering
%	\caption{{\bf Non-EUT Investor Decision Weights}: This figure illustrates the incorporation of non-EUT investor preferences in the decision between two investment portfolios used in the stochastic dominance analysis. The cumulative probability, p, of the rank order statistics of the portfolio returns are on the x-axis. The perceived utility weight, W(p,$\alpha$), or importance placed on the possibility of incurring a return with probability p. The parameter $\alpha$ measures EUT compliance, $\alpha$ = 1 when investors care equally about all returns and $\alpha$ < 1 when investors care about extreme loses more than they should".} \label{fig:sd_ill_graph}
%	\input{figures/sd_ill_plot}
%\end{figure}
Using many values of $\alpha$, I test the stochastic dominance of AV relative to SV. As \citet{hadar_rules_1969,hanoch_efficiency_1969,rothschild_increasing_1970,levy_experimental_2002} detail, the use of stochastic dominance tests allow us to make conclusions about the preference for AV or SV management for investors whose expected utility functions differ from simple mean-variance optimization. In results reported in the appendix, I use the bootstrap sampling methods detailed in \citet{vinod_h.d._ranking_2004,vinod_hands-intermediate_2008} to test the stochastic dominance of AV over SV to the forth order. Second order stochastic dominance, AV over SV, means that any risk averse investor would prefer AV. \citep{mcfadden_testing_1989,valle_novel_2017} Third order stochastic dominance means that any expected utility investor regardless of the form of the utility function would prefer AV to SV. \citep{whitmore_third-degree_1970,chan_third_2016} At forth order stochastic dominance, in addition to the concept of risk aversion both prudence and temperance are incorporated and all expected-utility theory (EUT) investors prefer AV management to SV. \citep{kimball_standard_1993,noauthor_risk-aversion_nodate} As table \ref{tab:tab_sd} shows, expected utility investors whose $\alpha$ equals 1 prefer AV management to SV management. The positive numbers in across columns SD2, SD3, and SD4 indicate up to forth order stochastic dominance. Moreover, investors with non-EUT, e.g. prospect theory, preferences still prefer AV management to SV. \citep{kahneman_prospect_1979} For all values of $\alpha$ AV management stochastically dominants to the forth order over the SV portfolio.
%\input{tables/performance/sd_utility}

\bigskip
\centerline{\bf [Place Table~\ref{tab:tab_sd} about here]}
\bigskip

I use the extensions in \citet{vinod_generalized_2016} to show that the preference for AV is robust to deviations from expected utility theory. AV is the preferred management strategy for investors who care about utility whether they adhere to strict expected utility or behaviorally stray. Table \ref{tab:tab_sd} shows the results of the dominance tests for values of $\alpha$ ranging from .99, a nearly completely EUT investor, to .01, a nearly completely non-EUT investor. All investors prefer AV managed returns.

%The return on the market portfolio is the return on the value-weighted representative average portfolio held by all investors. However, any investor subject to investment constraints or not, risk averse or tolerant benefits from switching from the SV managed portfolio to the AV managed portfolio. They benefit from switching from the market buy and hold to the AV managed portfolio even more. For the same level of variance risk they get far more return with better risk adjusted properties. How is it that this holds over nine decades of market history? Why is the average investor accepting the lessor return of the market portfolio?