The importance of the relationship of the stock market and aggregate wealth to the performance of the AV managed strategy should show up in the AV managed returns systematically. By the arguments made in \citet{pollet_average_2010} and implied in the sub-sample results above, AV management will under-perform where the stock market return is a smaller portion and less representative of returns to aggregate wealth. To test this hypothesis, I use Credit Suisse's annual reports on global wealth.\footnote{The reports are available for 2011 through 2017, covering data from 2000 to 2017, at https://www.credit-suisse.com/corporate/en/research/research-institute/global-wealth-report.html} Each year, starting in 2005, I rank countries on the ratio of annual market return to return on annual wealth. I then form portfolios long in the above median ratio countries, short in the below and a long minus short using both. For robustness, I also use GDP per capita as it often appears as a proxy in cross country studies of wealth and income effects. \citep{barro_cross-country_1989,levine_what_1993,baird_aggregate_2010} Thus, market capitalization to GDP per capita should serve as a useful, though imperfect, a proxy forthe proportion of aggregate wealth represented by the stock market. If the relationship of the proxy returns and aggregate wealth is systematically important to AV returns in the direction expected, the AV managed strategy should do better in countries with above median market to GDP ratio. Thus, a strategy long the high ratio countries and short the low ratio countries should have a positive and significant alpha. 

As seen in table \ref{tab:tab_intPerf1}, AV management produces positive returns across all countries so the performance of the long/short strategy will depend on the long side producing significantly better performance than the short. The long/short AV strategy performs just as expected. Using the Credit Suisse wealth numbers, investors capture average annualizedreturns over 12.6\% with a Sharpe ratio above .74 on the long side. Unfortunately in this case, performance is also strong on the short side where investors earn 7.5\%. The long/short portfolio nets investors better than 5\% annualized return with a Sharpe ratio better than the US buy and hold equity return. Moreover,the portfolio has a positive and significant Fama-French three, five-factor, and five-factor plus Momentumalphas meaning the relationship of the stock market to aggregate wealth is systematically important to AV management as seen in the pre-1962 results above. These results hold qualitatively for the market capitalization to GDP per capita sorting strategy as well.

The full in-sample regression monthly results support the conclusions reached by \citet{pollet_average_2010} at the quarterly frequency over a smaller window. Using the intuition in the argument for AC as a signal of systematic risk which depends on the relationship of the market index and aggregate wealth, I demonstrated a placebo-like sub-sample with an expected lack of results and a systematic difference in AV managed returns across countries. Each of these results suggest AV management works by allowing investors to time changes in the mix of systematic risk in market index variance. However, in-sample relationships are not sufficient to know that investors have access to the dynamics of this relationship in real-time. It is well documented that many in-sample strategies do not work out-of-sample.