The average variance managed portfolio produces significantly higher returns than the buy and hold market portfolio for the same level of total variance. As long as investors have access to either portfolio, there must be another investor untility generating aspect to the holding the market portfolio in order for this risk-return relationship to not violate modern portfolio theory. Either investors are compensated more for the market portfolio or penalized more for the AV portfolio in utility terms. A reasonable explaination can be taken from the literature on the cross section of the low-risk anonomaly associated with "lottery-like" stocks. Lottery stocks are known to generate lower future returns and this literature posits a lottery preference for some investors. \citep{barberis_stocks_2008} This preference suplements the utility from assets returns with a lottery dividend the investors receieves from holding positions in assets which provide the possiblity of very high returns with low probability. These investors optimize their holdings in the presence of a reward for holding assets that provide the same type of satisfaction or excitment as holding a lottery ticket or placing a wager. Another reasonable explaination is that investors are either prevented from or excessively penalized through costs for taking the leverage needed for either the AV or SV suggested holdings. This lending constraint explaination has a long history originating soon after the idea of mean-variance portfolio optimization.

\subsection{Changes to the Capital Market Line}
\input{the_cml}

\subsection{Lottery Preference}
\input{lottery_preference2}

\subsection{Lending Constraints}
\input{lending_constraints}